\Large \bf Frontrunning

### 2018-07-04 frontrunning/Latex/sections/paper.tex
[frontrunning] minor changes and added some notes

\textbf{Frontrunning in Blockchains}: The main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, everyone running a node of such blockchain could potentially have access to such information, hence it makes it much easier for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.

@@

@@

\subsection{Financial Markets}
%orders, exchanges
% @shayan: front runnign attacks on 0x and etherdelta . if one past one found add it to Implications!

@@

>>>>

% more on the definition in the wiki page: https://en.wikipedia.org/wiki/Front_running

% [optional but interesting] Here we can talk about Principal–agent problem: https://en.wikipedia.org/wiki/Principal%E2%80%93agent_problem

\textbf{Frontrunning in Blockchains}: One of the main discussion regarding regulations for exchanges on the topic of frontrunning, comes from the fact that information access is layered and some could be accessed only by insider actors, such as the broker, the IT administrator, \etc. In the blockchain world, everyone running a node of one blockchain could potentially have access to such information, hence it makes it is more susceptible for any actor to engage in frontrunning within applications running on the blockchain. Some other key differences are the fact that such actor can stay anonymous and also enforcing regulation is infeasible in traditional sense, however the decentral application could be designed in such a way to prevent frontrunning attacks.

@@

~\cite{malinova2017market}
~\cite{aune2017footprints}

@@

\subsection{Financial Markets}
%orders, exchanges
% @shayan: front runnign attacks on 0x and etherdelta . if one past one found add it to Implications!
% http://hackingdistributed.com/2017/08/13/cost-of-decent/

@@

% @Mahsa: some interesting read (check out the references) for domain name front running : https://en.wikipedia.org/wiki/Domain_name_front_running
